\section*{Abstract}
The search for new physics beyond the standard model of particle physics is one of the main goals of the CMS experiment at the CERN Large Hadron Collider. Many theories, for instance supersymmetry, involve the possible production of new coloured particles which feature jets as their experimental signature. Thus, it is important to have a good understanding of jet-related properties in order to allow such searches.\\
In the first part of this thesis, a measurement of the jet transverse-momentum resolution is presented. This is based on the analysis of proton-proton collision data recorded at a centre-of-mass energy of $\sqrt{s}=8$\tev by the CMS experiment. The measurement utilizes the transverse momentum balance of dijet events at particle level. The main focus is on the determination of the data-to-simulation ratio of the jet transverse-momentum resolution which can be used to correct the jet resolution in simulated events to match the one observed in data. This ratio has been determined with a significantly improved precision compared to previous analyses for the pseudorapidity range $0.0 \leq |\eta| \leq 5.0$. \\ 
The second part of the thesis focuses on searches for supersymmetry in final states with several jets and missing transverse momentum. A search performed with collision data recorded at $\sqrt{s}=8$\tev is presented which is mainly sensitive to the production of light-flavour squarks and gluinos as well as the gluino-mediated production of third generation particles. In this analysis, the main challenge arises from a precise determination of background contributions from standard model processes as the analysis is performed in an extreme kinematic phase space. In this thesis, a method to estimate QCD background contributions relying on the jet-\pt response is presented and necessary modifications for a correct prediction of high jet multiplicity events are introduced. In the analysis, results consistent with standard model expectations have been obtained and the production of light-flavour squarks below 780\gev and that of gluinos up to 1.1--1.2\tev has been excluded at $95\%$ confidence level for a mass of the lightest supersymmetric particle (LSP) not exceeding 100\gev in the context of simplified supersymmetric models. \\
Furthermore, a prospect study investigating different search strategies for the identification of direct pair production of stop quarks is shown. This is based on simulated events at a centre-of-mass energy of $\sqrt{s}=13$\tev. Utilizing algorithms for the identification of boosted hadronically decaying top quarks arising from the decay of heavy stop quarks, a search sensitivity of stop quark masses up to the 1\tev range can be obtained for LSP masses less than approximately 300\gev with the same integrated luminosity as recorded at $\sqrt{s}=8$\tev. This selection could improve the search sensitivity with respect to existing analyses. Moreover, the identified selection is also suitable to study gluino-mediated production of third-generation squarks and provides a complementary approach to existing multijet analyses.      
